A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-02-01 Article.qmd
-

    ID = c(1 : I);   
    var = list("ID" = ID, "Block" = Block, "Band" = Band, "Beet" = Beet, 
               "DPT" = DPT);

    data = f_var(var)

@@

col = c(paletteer_d("awtools::spalette", n = 5))[- c(2)]

>>>>

    ID = c(1 : I);

    data = expand_grid(ID = c(1 : I),   Block = c(1 : K),   Band = c(1 : J), 
                   Beet = c(1 : N),   DPT = seq(0, 12, length.out = T))

@@

col = c("#9F248FFF", "#017A4AFF", "#F9791EFF", "#244579FF")   # c(paletteer_d("awtools::spalette", n = 5))[- c(2)]
